Parallel Information Set Generation for Kriegspiel

### 2012-07-12 sbac/paper.tex
Removed some duplicate text

\label{speedups}
\vspace{-0.3in}
\end{table}
In order to understand the effect of various parameters such as grain size and load balancing, we first evaluated the scalability of our implementation using a randomly selected problem instance. Next, we show that our implementation performs equally well for instances from actual games.
\subsection{Analysis using Random Instance}
The performance results reported in
this section were obtained by running our program on Blueprint with up to 1024 processors. This system was composed of 120 POWER5+ nodes, each having 16 cores and 64GB of memory. The system was decomissioned in June 2011 and is no longer in operation.

Table~\ref{speedups} shows the performance results for our algorithm on a randomly selected problem instance in which
the size of the information set was about 4.5 million.  This instance is not necessarily representative of all games or
states of the game, but it was not cherry-picked in any way. The table shows that the problem is indeed highly
parallizable.  The speedups are nearly linear for up  to 32 processors, and even on 1024 processors, we get a good
speedup.  In this particular instance, the sequential algorithm takes almost 25 minutes to run.  But when parallelized
on 1024 processors---perfectly reasonable resource usage on modern hardware---the search takes less than three seconds.
This is a speedup of 576 times!  It might not be reasonable to use the algorithm at all if it takes 25 or more to run
for some turns.  But if the cost is only a few seconds, it becomes entirely feasible.

>>>>

\label{speedups}
\vspace{-0.3in}
\end{table}
